\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}.

@@

\end{algorithmic}
\caption{Original Softmax and Beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{algorithm}

@@

Thirdly, we are only interested in the best class. Since the best class is known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

\caption{Fused softmax and argmax}
\label{algo:Fused Kernel}
\end{algorithm}

>>>>

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-best is a simple extension of this.

@@

\end{algorithmic}
\caption{Original softmax and beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{algorithm}

@@

Thirdly, we are only interested in the probabilities of the best classes. Since these classes are known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

\caption{Fused softmax and beam search}
\label{algo:Fused Kernel}
\end{algorithm}
